---
title: "Agricultural Statistics"
author: "Hadrien"
date: "3/27/2019"
output: html_document
---

# Overview 

This analysis aims to better understand agricultural production trends in order to better guide decisions related to the business and ensure a future where all countries can achieve food security.


**Data:** Data for this analysis was obtained from the [Food and Agricultural Organization of the United Nations](http://www.fao.org/faostat/en/#data/QC) website on April 1st, 2019. Data was downloaded as the bulk download "All Data".

```{r setup, include=FALSE}
# set default settings for all code chunks
knitr::opts_chunk$set(message=FALSE, warnings=FALSE)
```


```{r tidy-data, include=FALSE}

######################
# load and tidy data #
######################

library(tidyverse)
library(readr)

# load data
df <- read_csv("data/Production_Crops_E_All_Data_NOFLAG.csv")

# transform from wide to long format
df <- df %>% gather(Year, Value, Y1961:Y2017)

# clean up year
df$Year <-  df$Year %>% str_remove("Y") %>% as.integer()

```



```{r, echo=FALSE}

######################################
# Top production by crop (worldwide) #
######################################

library(choroplethr)

# remove aggregates and yield

df <- df %>% 
  filter(Element == "Production", !grepl("Total|Primary|Rice Milled Eqv", Item))

df_total_production <-  df %>%
  group_by(Item) %>%
  summarise(tonnes_produced = sum(na.omit(Value)))

ggplot <- df_total_production %>%
  top_n(20, tonnes_produced) %>%
  ggplot(aes(reorder(Item,-tonnes_produced), tonnes_produced)) + geom_bar(stat =
                                                                            "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

# demonstrate default options
data(df_pop_country)
country_choropleth(c("USA", "Canada"), c(100,50))


```


## Production trend

<div style="float:right; margin-left: 10%;">
 
```{r,echo=FALSE, fig.width=6}
crop <- "Wheat"
country <- "Canada"

# plot production by crop and country
df %>%
  filter( Item == crop, Area == country) %>%
  ggplot(aes(Year,Value)) + geom_point() +
  geom_smooth() + 
  ggtitle(label = "Annual Production (in tonnes)")
```

 </div>
 
[Insert country name  here](https://en.wikipedia.org/wiki/Canada) is 

country stats: https://cran.r-project.org/web/packages/wbstats/vignettes/Using_the_wbstats_package.html
 